### 2013-06-14 replies.tex

@@

@@

@@

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly}}

@@

@@

>>>>

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is a basic
postulate of the niche model. We have added a reference to the original paper to
eliminate ambiguity.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The
  \emph{dotted} lines. We corrected accordingly and apologize for the mistake.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{No. The centroid
is a function of the two body sizes (hence $\alpha$), while the range limits are
a function of the predator body size and its range.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{Whether the
correct prediction of absence or presence of an interaction is the most
interesting part of a model is ultimately a matter of personal taste, and
adequation to the study objectives. Given that (especialyl when no other traits
than body size are included), this method tends to over-estimate the number of
links, we argue that correctly predicting absences of links is an extremely
important feature.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
accordingly.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We argue it is an
important piece of information, which was required by a previous reviewer. We
made no changes.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The fact that our
model over-predict the number of interactions is abundantly discussed in the
manuscript (along with why, and how to overcome it), so we will not elaborate
further on it in this reply. In the original niche model paper, it is true
that $c$ is not constrained by $n$. However, the purposes of the two models are
not the same. The niche model allows to generate a distribution of network
properties based only on connectance and richness. We add allometric
informations so as to be able to estimate species-level interactions in addition
to network properties. The allometric relationshipss on which we rely are well
documented. As for the fact that other traits can be added, this is discussed in
the manuscript at several places, including a whole figure. We made no changes
to the manuscript.}}
